Effect of character correlation

### 2017-07-25 Analysis/EffectCorrelation.Rmd
Added aov analysis

```{r, eval = TRUE, message = FALSE}
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")
```

@@

>>>>

```{r, eval = TRUE, message = FALSE}
library(dispRity)
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")
```

@@

Some stats
-----------------------------------

```{r}
## Getting the whole data
whole_data <- list("t25" = t25_list, "t75" = t75_list, "t150" = t150_list)

## getting the aov data
aov_data <- get.aov.data(whole_data, "RF", "norm", combined = TRUE)

## with lme4
library(lme4) ; library(lmerTest)

## NTS function of scenario (random = method + taxa + character)
model <- lmer(NTS ~ scenario + (1|method/taxa/character), data = aov_data$data)
anova(model)
difflsmeans(model, test.effs = "scenario")

## Plotting the residuals
normal_test <- shapiro.test(residuals(model))
hist(residuals(model),
    main = paste("Normal (W=", round(normal_test$statistic, digit = 2) ,
        "; p=", round(normal_test$p.value, digit = 2) ,")", sep = ""))

## Residuals vs predicted plot
plot(fitted(model), residuals(model))

## The residuals seem
```

```{r, fig.width=12, fig.height=6}
op <- par(mfrow=c(1,2))
## Plotting the residuals
normal_test <- shapiro.test(residuals(model))
hist(residuals(model),
    main = paste("non-normal (W=", round(normal_test$statistic, digit = 2) ,
        "; p=", round(normal_test$p.value, digit = 2) ,")", sep = ""))

## Residuals vs predicted plot
homo_test <- bartlett.test(NTS ~ scenario, data = aov_data$data)
plot(fitted(model), residuals(model),
    main = paste("heterodastic (Bartlett K^2=", round(homo_test$statistic, digit = 2) ,
        "; p=", round(homo_test$p.value, digit = 2) ,")", sep = ""))
par(op)
```

The results seem to be heterodastic

Supp
-----------------------------------
